A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-02 paper/elsarticle/elsarticle-template.tex
Update elsarticle-template.tex

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to view the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. Spatial AR is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with head-mounted displays, but by projection to the scene itself \cite{bimber2019spatial}, thus eliminating both aforementioned problems. Yet considering for the moment a planar surface to be augmented, unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the projected image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction, often using software bundled with the projector.

>>>>

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to view the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. Spatial AR is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with head-mounted displays, but by projection to the scene itself \cite{bimber2019spatial}, thus eliminating both aforementioned problems. Yet considering for the moment a planar surface to be augmented, unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the projected image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction to appropriately warp the image to be projected, often using software bundled with the projector.
